---
author: "Qiran Chen"
title: "p8105_hw3_qc2336"
output: html_document
date: "2023-10-10"
---

```{r}
library(tidyverse)
library(ggplot2)
```

## Problem 1


```{r}
library(p8105.datasets)
data("instacart")
data("brfss_smart2010")
```

```{r}
tail(instacart,5)
summary(instacart)
instacart|> 
  count(user_id)
```
>> This data has 1384617 observeations. Including 15 variables order id, user id,product d, aisle id departmen id, aisle, department order number, days since prior order, order time, product name and if it is reordered. There are 131209 unique user id in the data.


```{r}
instacart|>
  count(aisle,name="n_items")|>
  arrange(desc(n_items))

```
>> There are 134 aisle in the instacart dataset. The most items order aisle is fresh vegetable.

```{r}
instacart|>
  count(aisle,name="n_items")|>
  filter(n_items>10000)|>
  mutate(aisle=fct_reorder(aisle,n_items))|>
  ggplot(aes(x=aisle,y=n_items))+
  geom_point()+
  theme(axis.text.x = element_text(angle = 65, vjust = 1, hjust=1))+
  ggtitle("Number of Items in Each Aisle")
  
```

```{r}
top3_product=instacart|>
  filter(aisle==c('baking ingredients', 'dog food care', 'packaged vegetables fruits'))|>
  group_by(aisle)|>
  count(product_name, sort=TRUE)|>
  top_n(3)

  
top3_product
```


```{r}
coffee_apple=instacart|>
  filter(product_name==c("Pink Lady Apples", "Coffee Ice Cream"))|>
  mutate(order_dow=factor(order_dow, labels = c("Monday","Tueday","Wednesday","Thursday","Friday", "Saturday", "Sunday")))|>
  group_by(product_name,order_dow)|>
  summarize(mean_time=mean(order_hour_of_day))|>
  pivot_wider(names_from = order_dow,
              values_from = mean_time)
coffee_apple
  
```
## Problem 2

```{r}
brfss_smart_df=brfss_smart2010|>
  janitor::clean_names()|>
  rename(states_abbrev=locationabbr,
         states_county=locationdesc,
         responde_id=respid)|>
  filter(topic=="Overall Health")|>
  mutate(response=factor(response,
                         levels=c("Poor","Fair","Good","Very good","Excellent")))

brfss_smart_df

```
```{r}

brfss_smart_df|>
  filter(year=="2002")|>
  group_by(states_abbrev)|>
  summarize(n_location=n_distinct(states_county))|>
  filter(n_location >=7)

brfss_smart_df|>
  filter(year=="2010")|>
  group_by(states_abbrev)|>
  summarize(n_location=n_distinct(states_county))|>
  filter(n_location >=7)

```
>> There are 6 states observed in 2002, and 14 states in 2010.

```{r}
brfss_smart_df|>
  filter(response=="Excellent")|>
  group_by(year, states_abbrev)|>
  summarize(mean_data_value=mean(data_value))|>
  ungroup()|>
  ggplot(aes(x=year,y=mean_data_value, color=states_abbrev, na.rm= TRUE))+
  geom_line()+
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=0.2))+
  labs( title = "Mean Data Value Overtime within the states") 
  
```
>>This result shows the mean data value over time with in the state.

```{r}
brfss_smart_df|>
  filter(year==c("2006","2010"),states_abbrev=="NY")|>
  ggplot(aes(x=response,y=data_value,color=response))+
  geom_boxplot(binwidth = 0.5)+
  facet_grid(.~year)
  
  
  
```


## Problem 3


```{r}
covar<-read_csv("./nhanes_covar.csv",skip=4)
accel<-read_csv("./nhanes_accel.csv")
```

```{r}
covar=covar|>
  drop_na()|>
  filter(age>=21)|>
  mutate(education=factor(education,labels=c("Less than High School", "High School", "More than High School")),
         sex=factor(sex,labels=c("male","female")))
covar
```

```{r}
covar|>
  group_by(education)|>
  count(sex)
covar|>
ggplot(aes(x=sex,y=age,color=sex))+
  geom_boxplot()+
  facet_grid(.~education)+
  ggtitle("Age Distribution of Male and Female in Different Education Levels")
```
>> The table shows there are more male and female who has a more than high school, the age distribution shows they are younger in age. Male and Female who had less than high school and high school education are relatively similar in number.The mean age of Less than high school is older than the other two. The high school education male and female has a more salient difference in age.


